Automatic Code Cleaning in R with `Rclean`

### 2020-03-13 ropensci/rclean_technote.Rmd
Spellcheck

The `R` language has become very popular among scientists and analysts
because it enables the rapid development of software and empowers
scientific investigation. However, regardless of the language used,
data analysis is usually complicated. Because of various project
complexities and time contraints, analytical software often reflects
these challenges. "What did I measure? What analyses are relevant to
them? Do I need to transform the data? What's the function for the
analysis I want to run?" Although many researchers see the value in
learning to write software, the time investment for learning a
programming language alone is still exceedingly high for many, let
alone also learning software best practices. The downside to the rapid
spread of data science is that learning to create good software takes
a back-seat to just writing code that will get the job "done" leading
to issues with transparency and software that is highly unstable
(i.e. buggy and not reproducible).

The goal of `Rclean` is to provide a automated tool to help scientists
more easily write better code. Specifically, `Rclean` has been
designed to faciliate the isolation of the code needed to produce one
or more results, because more often then not, when someone is writing
an R script, the ultimate goal is analytical results for inference,
such as a set of statistical analyses and associated figures and
tables. As the investigative process is inherently iterative, this set
of results is nearly always a subset of a much larger set of possible
ways to explore a dataset. There are many statistical tests and
visualizations and other representations that can be employed in a
myriad of ways depending on how the data are processed. This commonly
leads to lengthy, complicated scripts from which researchers manually
subset results, but likely never to be refactored because of the
difficulty in disentangling the code.

>>>>

The `R` language has become very popular among scientists and analysts
because it enables the rapid development of software and empowers
scientific investigation. However, regardless of the language used,
data analysis is usually complicated. Because of various project
complexities and time constraints, analytical software often reflects
these challenges. "What did I measure? What analyses are relevant to
them? Do I need to transform the data? What's the function for the
analysis I want to run?" Although many researchers see the value in
learning to write software, the time investment for learning a
programming language alone is still exceedingly high for many, let
alone also learning software best practices. The downside to the rapid
spread of data science is that learning to create good software takes
a back-seat to just writing code that will get the job "done" leading
to issues with transparency and software that is highly unstable
(i.e. buggy and not reproducible).

The goal of `Rclean` is to provide a automated tool to help scientists
more easily write better code. Specifically, `Rclean` has been
designed to facilitate the isolation of the code needed to produce one
or more results, because more often then not, when someone is writing
an R script, the ultimate goal is analytical results for inference,
such as a set of statistical analyses and associated figures and
tables. As the investigative process is inherently iterative, this set
of results is nearly always a subset of a much larger set of possible
ways to explore a dataset. There are many statistical tests and
visualizations and other representations that can be employed in a
myriad of ways depending on how the data are processed. This commonly
leads to lengthy, complicated scripts from which researchers manually
subset results, but likely never to be refactored because of the
difficulty in disentangling the code.
